---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(tidyverse)
library(rtracklayer)
library(ggplot2)
library(plotly)
setwd("~/Documents/10T_K36me_March_2023")
```

```{=html}
<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }

</style>
```

# PCA

Using log2 enrichment over input matrix as input to PCA (after scaling/centering)

## Single KO {.tabset}

### All

We see a batch effect between Gerry's and Chao's samples.
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/singleKO_with_Chao.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

### Sans Chao's samples
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/singleKO_no_Chao.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

---

## Multiple knockouts {.tabset}

### All
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/multipleKO_with_Chao.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

### Sans Chao's samples
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/multipleKO_without_Chao.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

---

## Overexpression {.tabset}

### With multiple KOs

Here we see NSD3-OE clustering with NSD12DKO whereas NSD1/2-OE clustering with QKO/QuiKO
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/multipleKO_with_OE.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

### Only OE samples

Here we start to see clustering according to the NSD enzyme that is being overexpressed, albeit NSD1/2-OE samples cluster together whereas NSD3-OE samples clusters separately
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/OE.RData")
pd <- p$data
ggplotly(p,source = "select",tooltip = c("samp","batch"))
```

---

# Correlation

## Single KO {.tabset}

### All {.tabset .tabset-pills}

#### Pearson
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/singleKO_with_Chao_pearson.RData")
hm %>%
  layout(height = 900)
```
:::

#### Spearman
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/singleKO_with_Chao_spearman.RData")
hm %>%
  layout(height = 900)
```
:::

### Sans Chao's samples {.tabset .tabset-pills}

#### Pearson
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/singleKO_no_Chao_pearson.RData")
hm %>%
  layout(height = 900)
```
:::

#### Spearman
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/singleKO_with_no_spearman.RData")
hm %>%
  layout(height = 900)
```
:::

---

## Multiple KOs {.tabset .tabset-pills}

### Pearson
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/multipleKO_no_Chao_pearson.RData")
hm %>%
  layout(height = 500)
```

### Spearman
```{r,echo = FALSE, warning=FALSE,message=FALSE,out.width='100%'}
load("data/multipleKO_with_no_Chao_spearman.RData")
hm %>%
  layout(height = 500)
```

---

## Overexpression {.tabset}

### With multiple KOs {.tabset .tabset-pills}

#### Pearson
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=10,fig.height=6}
load("data/multipleKO_with_OE_pearson.RData")
hm %>%
  layout(height = 900)
```
:::

#### Spearman
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=10,fig.height=6}
load("data/multipleKO_with_OE_spearman.RData")
hm %>%
  layout(height = 900)
```
:::

### Only OE samples {.tabset .tabset-pills}

#### Pearson
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/OE_pearson.RData")
hm %>%
  layout(height = 500)
```
:::

#### Spearman
::: superbigimage
```{r,echo = FALSE, warning=FALSE,message=FALSE,fig.width=9,fig.height=6}
load("data/OE_spearman.RData")
hm %>%
  layout(height = 500)
```
:::